Tables with \textbf{xtable} and \textbf{knitr}

### 2016-11-03 src/ArticleReadyTableGenerate.Rnw
some cleanup, working multicolumn names for pooled LCDM

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE>>=
  class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @

@@

<<diag.plot.ICV_1,fig.show='hide',results='asis',echo=FALSE>>=
#Gender, age, ICV, ED.year, hemisphere
library(ggplot2)
library(reshape2)
# Convert all.df to long format
#
all.df.lf<- melt(all.df[all.df$Wave1,], id.var=c(1,2,8,9,10,71),
                 measure.vars=11:40, value.name="LCDM.measure",variable.name="hemi.region.subregion.meas")

@@

<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE>>=
#print("subregion_sideway_table_summary_stats")
stat.tables.for.regions <- list()
summ.stats.tables<-list(stg=list(),mtg=list(),itg=list(),postcing=list(),antcing=list())
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  all.df.lf.stg    <- filter(all.df.lf, region==region.for.table)

@@

  all.df.lf.stg.lh$aggstat<- as.factor(all.df.lf.stg.lh$aggstat)
  all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
  all.df.lf.stg.rh.grp<- group_by(all.df.lf.stg.rh, aggstat, sex,Diag)

@@

      xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
      p_val_table_list[[side]]<- p_value_table_print
      xtablelist[[side]]<-xtab.out
    }
    attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
    xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""))
    col.names <- c("KS test","MWU test", "Welch's t-test")
    # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
    rowcom <- list()
    rowcom$pos = list(-1)
    rowcom$command = paste0(paste0("Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse='')," \\\\ " ,collapse="")
    print(rowcom$command)
    xtablelist.out<-print(xtablelist, only.contents=FALSE,
      include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
      type="latex",floating.environment = "sidewaystable", print.results = FALSE)
    second_heading <- "(\\\\begin\\{tabular\\}.*)" 
    xtablelist.out <- gsub( xtablelist.out, pattern = second_heading, perl =  TRUE,fixed=FALSE,
    replacement =  paste0( "\\1", "\n", rowcom$command, collapse = '') )
    cat(xtablelist.out,sep="\n")
  }

>>>>

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE,message=FALSE,warning=FALSE>>=
  class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @

@@

<<diag.plot.ICV_1,fig.show='hide',results='asis',echo=FALSE,message=FALSE,warning=FALSE>>=
#Gender, age, ICV, ED.year, hemisphere
library(ggplot2)
library(reshape2)
# Convert all.df to long format
#
all.df.lf<- melt(all.df[all.df$Wave1,], id.var=c(1,2,8,9,10,71),
                 measure.vars=11:40, value.name="LCDM.measure",variable.name="hemi.region.subregion.meas")

@@

<<subregion_sideway_table_summary_stats,eval=TRUE,echo=FALSE,message=FALSE>>=
#print("subregion_sideway_table_summary_stats")

library(dplyr)

stat.tables.for.regions <- list()
summ.stats.tables<-list(stg=list(),mtg=list(),itg=list(),postcing=list(),antcing=list())
for (region.for.table in c("stg" ,"mtg","itg","postcing","antcing")){
  all.df.lf.stg    <- filter(all.df.lf, region==region.for.table)

@@

  all.df.lf.stg.lh$aggstat<- as.factor(all.df.lf.stg.lh$aggstat)

  all.df.lf.stg.rh$aggstat<- as.factor(all.df.lf.stg.rh$aggstat)

  all.df.lf.stg.lh.grp<- group_by(all.df.lf.stg.lh, aggstat, sex,Diag)
  all.df.lf.stg.rh.grp<- group_by(all.df.lf.stg.rh, aggstat, sex,Diag)

@@

      xtab.out <- xtable( as.data.frame(p_value_table_print  ) )
      p_val_table_list[[side]]<- p_value_table_print
      xtablelist[[side]]<-xtab.out
    }
    attr(p_val_table_list, "subheadings") <- paste0("Hemisphere : ",c("Left","Right"))
    xtablelist <- xtableList(p_val_table_list, caption = paste0("Hypothesis Tests based on pooled LCDM statistics for ",region,collapse= ""),
                             align = 'l|ccc|ccc|ccc')
    col.names <- c("KS test","MWU test", "Welch's t-test")

    # Region & \multicolumn{3}{l}{KS test} & \multicolumn{3}{l}{MWU test} & \multicolumn{3}{l}{Welch's t-test}\\
    rowcom <- list()
    rowcom$pos = list(-1)
    rowcom$command = paste0(paste0(" Region",paste0(" & \\\\multicolumn{3}{c}{", col.names , '}', collapse=''),collapse=''))
    #print(rowcom$command)
    xtablelist.out<-print(xtablelist, only.contents=FALSE,
      include.rownames=TRUE, sanitize.colnames.function = simp.colnames,
      type="latex",floating.environment = "sidewaystable", print.results = FALSE,hline.after = c(-1))

    second_heading <- "(\\\\begin\\{tabular\\}.*\\})" 
    xtablelist.out <- gsub( xtablelist.out, pattern = second_heading, perl =  TRUE,fixed=FALSE,
    replacement =  paste0( "\\1", "\n", rowcom$command,' ','\\',' \\ ', collapse = '') )
    xtablelist.out <- gsub( xtablelist.out, pattern = '\\hline',fixed=TRUE,
    replacement =  paste0( "\\\\ \\hline", collapse = '') )
    #print (xtablelist.out)
    cat(xtablelist.out,sep="\n")
  }
